The Accuracy of KNN, SVM, neural network, naive Bayes classifier and DBSCAN, kmeans for Determining the Cancer by Gene-expression signatures And the Arrhythmia Types

### 2023-05-27 final/paper/main.tex
update parper

\usepackage{boxedminipage}
\usepackage{enumerate}
\usepackage{multirow}
\usepackage{url}
\usepackage{times}
\usepackage{version}
% \usepackage[pdftex]{graphicx}
\usepackage{graphicx} 
\usepackage{epsfig}
\usepackage{epsf}
%\usepackage{graphics}
\usepackage{caption}
\usepackage{subfigure}
\usepackage{algorithm}
\usepackage{algpseudocode}
%\PassOptionsToPackage{bookmarks={false}}{hyperref}
%%%%%%%%%%%%
\usepackage{comment}
\usepackage{multicol}
\usepackage{booktabs}
\usepackage{dblfloatfix}
% ==========================
%\usepackage[a4paper, margin = 2.5cm]{geometry}

@@

\title{The Accuracy of KNN, SVM, neural network, naive Bayes classifier and DBSCAN, kmeans for Determining the Cancer by Gene-expression signatures}

@@

\section*{Abstract}
Nowadays, using machine to give an early diagnosis of a cancer type is widely studied. 
In this paper, based on the gene-expression dataset on Synapse.org, we compare the performance of machine 
learning techniques, including data preprocessing, 
e.g., Principal components analysis (PCA), Autoencoder (AE), classification, e.g., k-nearest neighbors (KNN), 
support vector machine (SVM), neural network (NN), and clustering for dealing with unknown types, 
e.g., k-means, density-based spatial clustering of applications with noise (DBSCAN). 
The experiment results show that with PCA reducing the dimension of the dataset to 32, using KNN for classifying
the known types, and finally use DBSCAN to cluster the unknown types, the accuracy of predicting can 
reach about 94\%, which beats the other methods out.

breast invasive carcinoma (BRCA)
colon adenocarcinoma (COAD)
kidney renal clear cell carcinoma (KIRC)
lung adenocarcinoma (LUAD)
prostate adenocarcinoma (PRAD)

@@

In real application, besides from the konwn cancers in the train data, there're numerous unkown types of cancers. 
When a new type of cancer appears, how shall the machine results? In ideal situation, this new type of cancer should be 
reported as an unkonwn type, which can be done by the combination of classification and clustering. 
However, how to choose the proper machine learning methods is a hot potato, since the different combinations 
of machine learning methods have different performance.

In this work, the dataset on Synapse.org is used, which contains 20531 RNA sequences and 3 types of cancer 
in the train data, and 2 new types in test data. To find out which techniques is more suitable to predict 
cancer by RNA sequence, this work examines the the accuracy of the combinations of some major machine 
learning techniques, including PCA, AE, KNN, SVM, NN, k-means, DBSCAN.

@@

\bf{Autoencoder (AE)}: \rm{An} AE is a type of neural network used for unsupervised 
learning and dimensionality reduction. It is designed to learn efficient representations or encodings of 
input data by training the network to reconstruct its own inputs. The AE consists of an encoder 
and a decoder. The encoder compresses the input data into a lower-dimensional representation, often called 
the latent space or code. The decoder then aims to reconstruct the original input data from this compressed 
representation. By learning a compact representation of the input data, AEs can capture important features 
and discard noise or irrelevant information. This makes them effective in tasks such as image or 
text classification, where reducing the dimensionality of the data can improve performance.

\bf{Principal components analysis (PCA)}: \rm{PCA} is a statistical technique used for dimensionality 
reduction and data exploration. It aims to transform a dataset with a large number of variables into 
a lower-dimensional space while preserving the most important information. PCA accomplishes this by 
identifying the principal components, which are linear combinations of the original variables. 
Applications of PCA span various fields, including image and signal processing, finance, genetics, 
and social sciences. It is particularly useful in scenarios where the dataset is high-dimensional 
and the interpretation and visualization of the data are challenging.

@@

\bf{neural network (NN)}: \rm{Neural} network have been used in many fields to deal with intricate datas. With input layer, hidden 
layer and output layer constructed by neurons, each data in dataset is processed while passing through neurons, layer by layer. 
After the processing, the outcome can be used to predict.Using back propogation, the accuracy of predictions increase in each 
training. In order to construct the hidden layer more efficient, NAS(Neural Arcitecture Searching) is used to search suitable 
structure for hidden layer, increasing the accuracy. According to \cite{Gadekallu2020}\cite{Beghriche2021}, many neural network 
have been constructed and trained already, with high efficiency and accuracy in prediction of diabetes.

@@

\bf{k-means}: \rm{k-means} is a popular and easily implemented clustering method in machine learning and data analysis. With $n$
data points in a dataset, k-means algorithm partition them into $k$ distinct clusters. The algorithm works iteratively and 
converges to a solution by minimizing the sum of squared distance between the data points and the center of their cluster. 
K-means is a useful algorithm for clustering data, which is widely applied on many researches, e.g. \cite{oyelade2010application}, 
\cite{NIDHEESH2017213}, \cite{kadhm2018accurate}.

@@

\section{main section}

\section{Experiment result}
  \begin{table*}[htb]
    \newcommand{\z}{\phantom{0}}
    \caption{\textsc{Comparison of Classification Techniques. (Arrhythmia data set)}}
      \vspace{-\baselineskip}
    \resizebox{\textwidth}{!}{
      \begin{tabular}{@{}lccccccccl@{}}\toprule
      Method                    & Search (s) & acc                               & acc (normalized)             & acc (PCA-32)                & acc (PCA-32-normalized)    & acc (AE-32)            & acc (AE-32-normalized) \\ \midrule
      KNN-Brute-Force + DBSCAN  & $0.014$    & $44.3038 \pm 0$                   & $46.8354 \pm 0$              & $38.6076 \pm 0$             & $42.4051\pm 0$             & $34.8101 \pm 0$        & $44.3038 \pm 0$\\
      SVM (linear) + DBSCAN     & $1.048$    & $25.9494 \pm 0$                   & $35.4430 \pm 0$              & $32.2785 \pm 0$             & $29.7468 \pm 0$            & $31.6456 \pm 0$        & $27.8481 \pm 0$\\
      SVM (polynomial) + DBSCAN & $0.765$    & $25.9494 \pm 0$                   & $25.3165 \pm 0$              & $1.2658 \pm 0$              & $33.5443 \pm 0$            & $30.3797 \pm 0$        & $30.2785 \pm 0$\\
      SVM (RBF) + DBSCAN        & $5.298$    & $25.9494 \pm 0$                   & $22.7848 \pm 0$              & $0.6329 \pm 0$              & $30.3797 \pm 0$            & $22.1519 \pm 0$        & $34.1772 \pm 0$\\
      SVM (sigmoid) + DBSCAN    & $2.298$    & $28.4810 \pm 0$                   & $20.2532 \pm 0$              & $30.3797 \pm 0$             & $36.0759 \pm 0$            & $22.1519 \pm 0$        & $24.6835 \pm 0$\\
      KNN-Brute-Force + kmeans  & $0.014$    & $53.1646 \pm 0$                   & $50.6329 \pm 0$              & $43.0380 \pm 0$             & $43.0380 \pm 0$            & $36.0759 \pm 0$        & $41.7722 \pm 0$\\
      SVM (linear) + kmeans     & $X$        & $25.3165 \pm 0$                   & $37.9747 \pm 0$              & $25.3165 \pm 0$             & $27.8481 \pm 0$            & $24.0506 \pm 0$        & $20.2532 \pm 0$\\
      SVM (polynomial) + kmeans & $X$        & $25.3165 \pm 0$                   & $26.5823 \pm 0$              & $14.5570 \pm 0$             & $28.4810 \pm 0$            & $24.0506 \pm 0$        & $25.3165 \pm 0$\\
      SVM (RBF) + kmeans        & $X$        & $8.8608 \pm 0$                    & $29.7468 \pm 0$              & $0.6329 \pm 0$              & $1.2658 \pm 0$             & $22.7848 \pm 0$        & $27.2152 \pm 0$\\
      SVM (sigmoid) + kmeans    & $X$        & $22.6582 \pm 0$                   & $17.7848 \pm 0$              & $25.3165 \pm 0$             & $12.0253 \pm 0$            & $17.7215 \pm 0$        & $28.4810 \pm 0$\\
      \bottomrule
      \end{tabular}
    }
    \label{table:Arrhythmia_result}
      \vspace{-\baselineskip}
  \end{table*}

  \begin{table*}[htb]
    \newcommand{\z}{\phantom{0}}
    \caption{\textsc{Comparison of Classification Techniques. (gene expression cancer RNA-Seq data set)}}
      \vspace{-\baselineskip}
    \resizebox{\textwidth}{!}{
      \begin{tabular}{@{}lccccccccl@{}}\toprule
      Method                    & Search (s) & acc                               & acc (normalized)             & acc (PCA-30)                & acc (PCA-30-normalized)    & acc (AE-30)            & acc (AE-30-normalized)\\ \midrule
      KNN-Brute-Force + DBSCAN  & $4.317$    & $59.0361 \pm 0$                   & $66.5663 \pm 0$              & $94.5783 \pm 0$             & $78.3133 \pm 0$            & $64.4578 \pm 0$        & $59.3373 \pm 0$\\
      SVM (linear) + DBSCAN     & $131.809$  & $61.7470 \pm 0$                   & $9.9398 \pm 0$               & $9.9398 \pm 0$              & $10.5422 \pm 0$            & $63.2530 \pm 0$        & $13.5542 \pm 0$\\
      SVM (polynomial) + DBSCAN & $31.221$   & $61.7470 \pm 0$                   & $1.2048 \pm 0$               & $64.4578 \pm 0$             & $61.1446 \pm 0$            & $63.2530 \pm 0$        & $50.3012 \pm 0$\\
      SVM (RBF) + DBSCAN        & $3.988$    & $X$                               & $X$                          & $9.9398 \pm 0$              & $63.2530 \pm 0$            & $40.3614 \pm 0$        & $49.6988 \pm 0$\\
      SVM (sigmoid) + DBSCAN    & $0.446$    & $X$                               & $X$                          & $71.6867 \pm 0$             & $65.9639 \pm 0$            & $44.2771 \pm 0$        & $38.2530 \pm 0$\\
      KNN-Brute-Force + kmeans  & $4.859$    & $74.0964 \pm 0$                   & $53.6145 \pm 0$              & $94.8795 \pm 0$             & $84.9398 \pm 0$            & $42.1687 \pm 0$        & $65.9639 \pm 0$\\
      SVM (linear) + kmeans     & $X$        & $X \pm 0$                         & $X \pm 0$                    & $X \pm 0$                   & $X \pm 0$         & $0 \pm 0$                    & $0 \pm 0$\\
      SVM (polynomial) + kmeans & $X$        & $X \pm 0$                         & $X \pm 0$                    & $X \pm 0$                   & $X \pm 0$         & $0 \pm 0$                    & $0 \pm 0$\\
      SVM (linear) + kmeans     & $X$        & $X \pm 0$                         & $X \pm 0$                    & $X \pm 0$                   & $X \pm 0$         & $0 \pm 0$                    & $0 \pm 0$\\
      SVM (sigmoid) + kmeans    & $X$        & $X \pm 0$                         & $X \pm 0$                    & $X \pm 0$                   & $X \pm 0$         & $0 \pm 0$                    & $0 \pm 0$\\
      \bottomrule
      \end{tabular}
    }
    \label{table:gene_expression_result}
      \vspace{-\baselineskip}
  \end{table*}

>>>>

\usepackage{boxedminipage}
\usepackage{enumerate}
\usepackage{multirow}
\usepackage{url}
\usepackage{times}
\usepackage{version}
% \usepackage[pdftex]{graphicx}
\usepackage{graphicx} 
\usepackage{epsfig}
\usepackage{epsf}
%\usepackage{graphics}
\usepackage{caption}
\usepackage{subfigure}
\usepackage{algorithm}
\usepackage{algpseudocode}
%\PassOptionsToPackage{bookmarks={false}}{hyperref}
%%%%%%%%%%%%
\usepackage{comment}
\usepackage{multicol}
\usepackage{booktabs}
\usepackage{dblfloatfix}
\usepackage{hyperref}
% ==========================
%\usepackage[a4paper, margin = 2.5cm]{geometry}

\algrenewcommand\alglinenumber[1]{\footnotesize #1}
\algnewcommand\algorithmicassume{\textbf{Assumption:}}
\algnewcommand\Assume{\item[\algorithmicassume]}

@@

\title{The Accuracy of KNN, SVM, neural network, naive Bayes classifier and DBSCAN, kmeans for Determining the Cancer by Gene-expression signatures And the Arrhythmia Types}

@@

\section*{Abstract}
Nowadays, using machine to give an early diagnosis of a cancer type is widely studied. 
In this paper, based on the gene-expression dataset on Synapse.org, we compare the performance of machine 
learning techniques, including data preprocessing, e.g., Principal components analysis (PCA), Autoencoder 
(AE), classification, e.g., k-nearest neighbors (KNN), support vector machine (SVM), neural network (NN), 
and clustering for dealing with unknown types, e.g., k-means, density-based spatial clustering of 
applications with noise (DBSCAN).

The result of gene dataset shows that, with PCA reducing the dimension of the dataset to 32, use KNN for 
classifying the known types, and finally apply DBSCAN on the remaining data, the accuracy of predicting 
can reach about 94\%, which beats the other methods out. In the other way, the result of arrhythmia 
dataset shows that, with raw data, use KNN and k-means, the highest accuracy of predicting can reach about 
53\%.

The source code can be found in \href{https://github.com/OEmiliatanO/CSE\_data\_mining}{here}.

@@

In real application, besides from the konwn diseases in the train data, there're numerous unkown types of diseases. 
When a new type of disease appears, how shall the machine results? In ideal situation, this new type of disease should be 
reported as an unkonwn type, which can be done by the combination of classification and clustering. 
However, how to choose the proper machine learning methods is a hot potato, since the different combinations 
of machine learning methods have different performance.

In this work, the dataset on Synapse.org is used, which contains 20531 RNA sequences and 3 types of cancer 
in the train data, i.e., kidney renal clear cell carcinoma (KIRC), breast invasive carcinoma (BRCA), 
lung adenocarcinoma (LUAD), and 2 new types in test data, i.e., colon adenocarcinoma (COAD), 
prostate adenocarcinoma (PRAD). And also, the dataset of arrhythmia is included, which caintains
8 types in train data, and 5 new types in test data. To find out which techniques is more suitable to fit 
these two datasets, this work examines the the accuracy of the combinations of some major machine 
learning techniques, including PCA, AE, KNN, SVM, NN, k-means, DBSCAN.

@@

\bf{Autoencoder (AE)}: \rm{An} AE is a type of neural network used for unsupervised 
learning and dimensionality reduction. It is designed to learn efficient representations or encodings of 
input data by training the network to reconstruct its own inputs. The AE consists of an encoder 
and a decoder. The encoder compresses the input data into a lower-dimensional representation, often called 
the latent space or code. The decoder then aims to reconstruct the original input data from this compressed 
representation. By learning a compact representation of the input data, AEs can capture important features 
and discard noise or irrelevant information \cite{lu2013speech}. This makes them effective in tasks such as 
image \cite{zhang2018better} \cite{lore2017llnet} \cite{cheng2018deep} or text classification \cite{xu2017variational} 
\cite{xu2019semisupervised}, where reducing the dimensionality of the data can improve performance.

\bf{Principal components analysis (PCA)}: \rm{PCA} is a statistical technique used for dimensionality 
reduction and data exploration. It aims to transform a dataset with a large number of variables into 
a lower-dimensional space while preserving the most important information. PCA accomplishes this by 
identifying the principal components, which are linear combinations of the original variables. 
Applications of PCA span various fields, including image \cite{ma2019dimension} \cite{YANG20021997} 
and signal processing \cite{6497960} \cite{castells2007principal}, genetics \cite{reich2008principal} 
\cite{novembre2008interpreting}. It is particularly useful in scenarios where the dataset is 
high-dimensional and the interpretation and visualization of the data are challenging.

@@

\bf{neural network (NN)}: \rm{Neural} network have been used in many fields to deal with intricate datas. 
With input layer, hidden layer and output layer constructed by neurons, each data in dataset is processed 
while passing through neurons, layer by layer. After the processing, the outcome can be used to predict. 
Using back propogation, the accuracy of predictions increase in each training. In order to construct the 
hidden layer more efficient, NAS(Neural Arcitecture Searching) is used to search suitable structure for 
hidden layer, increasing the accuracy. According to \cite{Gadekallu2020}\cite{Beghriche2021}, many neural 
network have been constructed and trained already, with high efficiency and accuracy in prediction of 
diabetes.

@@

\bf{k-means}: \rm{K-means} is a popular and easily implemented clustering method in machine learning and 
data analysis. With $n$ data points in a dataset, k-means algorithm partition them into $k$ distinct 
clusters. The algorithm works iteratively and converges to a solution by minimizing the sum of squared 
distance between the data points and the center of their cluster. K-means is a useful algorithm for 
clustering data, which is widely applied on many researches, e.g. \cite{oyelade2010application}, 
\cite{NIDHEESH2017213}, \cite{kadhm2018accurate}.

@@

\section{Main Process}
  The main algorithm to process the dataset is shown as below:
  \begin{algorithm}
    \caption{The Main Algorithm}\label{alg:main}
    \begin{algorithmic}[1]
      \Require $\text{Dataset}$
      \State $\text{Data}, \text{Labels} \gets \text{Dataset}$
      \State $\text{Data}' \gets \text{preprocess}(\text{Data})$
      \State $\text{Konwns}, \text{Unkonwns} \gets \text{classify}(\text{Data}')$
      \State $\text{Clusters} \gets \text{clustering}(\text{Unkonwns})$
      \State $\text{Accuracy} \gets \text{calacc}((\text{Konwns}, \text{Clusters}), \text{Labels})$
    \end{algorithmic}
  \end{algorithm}

  First, preprocess the dataset, e.g. normalize, apply PCA, apply AE. Second, classify the data after preprocessing. 
  With this step the konwn types and the unknown types will be separated by a certain criterion. This criterions will 
  be varied depending on the classification algorithm. For KNN, the criterion is distance and probability. More specifically, 
  assume a data point $x$, and the k-nearest data points are $p_1,...,p_k$. Only those points whose distance between 
  $x$ smaller than $L$ will be marked valid. Denote the valid data points as $p'_1,...p'_n$, and the corresponding 
  labels are $l_1,...,l_n$. If this data point satisifies Eq~\ref{eqn:KNN_prob}, mark it as unkown type.
  \begin{equation}
    \label{eqn:KNN_prob}
    \frac{\arg\max_{t\in\text{types}\{N(t)\}}}{n}<P
  \end{equation}
  where $P$ is a manunally set probability and $N(t)$ is the number of type $t$ in those $n$ valid data points.

  As for SVM, the criterion born in the designed. Since SVM is meant to be a binary classifier, the SVM classification 
  algorithm must be redesigned. As shown in Algo~\ref{alg:SVMs}. 
  \begin{algorithm}[h]
    \caption{The SVM Multi-classification Algorithm}\label{alg:SVMs}
    \begin{algorithmic}[1]
      \Require $\text{Train Data, Labels, Test Data}$
      \Assume $\text{Length}(\text{Train Data})=\text{Length}(\text{Labels})=N,\text{Length}(\text{Test Data})=M$
      \For{$t \text{ in Known Types}$}
        \For{$i \text{ in }[1,N]$}
          \If{$\text{Labels}[i]\neq t$}
            \State $\text{Labels}'[i] = +1$
          \Else
            \State $\text{Labels}'[i] = -1$
          \EndIf
        \EndFor
        \State $\text{SVM}[t].\text{fit}(\text{Train Data}, \text{Labels}')$
      \EndFor
      \For{$t \text{ in Known Types}$}
        \For{$i\text{ in }[1,M]$}
          \If{$\text{SVM}[t].\text{predict}() = +1$}
            \State $\text{Test Labels}[i] = t$
          \Else
            \State $\text{Test Labels}[i] = \text{UNKNOWN}$
          \EndIf
        \EndFor
      \EndFor
    \end{algorithmic}
  \end{algorithm}

  After classifying, the konwn types and unkonwn types are separated. The data marked as unkonwn types will be thrown 
  into clustering algorithm, e.g., DBSCAN, k-means. Subsequently, the process is completed.

\section{Experiment result}
  The experiment result of arrhythmia dataset is shown in Table~\ref{table:Arrhythmia_result}. And the result of gene 
  expression cancer RNA-Seq data set is in Table~\ref{table:gene_expression_result}.

  From the result, the fact that SVM performs worse than KNN can be seen. The main reason is because the multiple 
  classification SVMs method designed here can't separate well in most of types. Fig~\ref{fig:SVM_fail} illurates the 
  situation. For type 1 SVM, the negative/positive classification makes the data hard to separate, and also for type 
  2, 3, etc. This happens even when the kernel trick is applied, though the kernel trick sometimes ease the pain. 
  \begin{figure}[htb]
    \centering
    \includegraphics[scale=0.15]{assets/SVM_fail.pdf}
    \caption{An example that multiple SVMs fail}
    \label{fig:SVM_fail}
  \end{figure}
  In the other hand, KNN performs extraordinarily. In arrhythmia dataset, KNN with k-means in raw data gets 53.1646\% 
  accuracy, which is the highest accuracy comparing to others methods. And in gene expression cancer RNA-Seq dataset, 
  KNN with k-means in PCA data gets 94.8795\%. And KNN with DBSCAN performs well too. This method shows similar performance 
  in these two datasets, which also gets 94.5783\% in gene expression cancer RNA-Seq dataset PCA data.

  \begin{table*}[htb]
    \newcommand{\z}{\phantom{0}}
    \caption{\textsc{Comparison of Classification Techniques. (Arrhythmia dataset)}}
      \vspace{-\baselineskip}
    \resizebox{\textwidth}{!}{
      \begin{tabular}{@{}lcccccccccccc@{}}\toprule
        Method                    & \multicolumn{2}{c}{Raw}                     & \multicolumn{2}{c}{Normalized}   & \multicolumn{2}{c}{PCA-32}        & \multicolumn{2}{c}{PCA-32 Normalized} & \multicolumn{2}{c}{AE-32}        & \multicolumn{2}{c}{AE-32 Normalized} \\ 
        \cmidrule(lr){2-3}\cmidrule(lr){4-5}\cmidrule(lr){6-7}\cmidrule(lr){8-9}\cmidrule(lr){10-11}\cmidrule(lr){12-13}
                                  & Search (s) & acc                            & Search (s) & acc                 & Search (s) & acc                  & Search (s) & acc                      & Search (s) & acc                  & Search (s) & acc            \\ \midrule
      KNN-Brute-Force + DBSCAN    & $0.0285$   & $47.4684 \pm 0$                & $0.0254$   & $46.8354 \pm 0$     & $0.0070$   & $38.6076 \pm 0$      & $0.0071$   & $42.4051\pm 0$           & $0.0071$   & $\bf{37.9747} \pm 0$ & $0.0071$   & $\bf{44.3038} \pm 0$\\
      SVM (linear) + DBSCAN       & $1.7269$   & $25.9494 \pm 0$                & $8.9285$   & $35.4430 \pm 0$     & $0.2186$   & $32.2785 \pm 0$      & $0.8162$   & $29.7468 \pm 0$          & $0.2169$   & $31.6456 \pm 0$      & $0.1552$   & $27.8481 \pm 0$\\
      SVM (polynomial) + DBSCAN   & $0.9993$   & $25.9494 \pm 0$                & $1.6100$   & $25.3165 \pm 0$     & $0.1997$   & $\z{1.2658} \pm 0$   & $0.4577$   & $33.5443 \pm 0$          & $0.2402$   & $30.3797 \pm 0$      & $0.4924$   & $30.2785 \pm 0$\\
      SVM (RBF) + DBSCAN          & $0.9915$   & $25.9494 \pm 0$                & $1.4681$   & $22.7848 \pm 0$     & $1.4328$   & $\z{0.6329} \pm 0$   & $11.9417$  & $30.3797 \pm 0$          & $13.5147$  & $22.1519 \pm 0$      & $24.7346$  & $34.1772 \pm 0$\\
      SVM (sigmoid) + DBSCAN      & $3.5272$   & $28.4810 \pm 0$                & $6.4731$   & $20.2532 \pm 0$     & $1.5779$   & $30.3797 \pm 0$      & $0.9797$   & $36.0759 \pm 0$          & $0.5284$   & $22.1519 \pm 0$      & $0.8430$   & $24.6835 \pm 0$\\
      KNN-Brute-Force + kmeans    & $0.0236$   & $\bf{53.1646} \pm 0$           & $0.0343$   & $\bf{50.6329} \pm 0$& $0.0068$   & $\bf{43.0380} \pm 0$ & $0.0069$   & $\bf{43.0380} \pm 0$     & $0.0069$   & $36.0759 \pm 0$      & $0.0080$   & $41.7722 \pm 0$\\
      SVM (linear) + kmeans       & $1.7719$   & $25.3165 \pm 0$                & $37.9747$  & $37.9747 \pm 0$     & $0.2317$   & $25.3165 \pm 0$      & $0.8932$   & $27.8481 \pm 0$          & $0.2331$   & $24.0506 \pm 0$      & $0.1596$   & $20.2532 \pm 0$\\
      SVM (polynomial) + kmeans   & $1.0456$   & $25.3165 \pm 0$                & $1.4942$   & $26.5823 \pm 0$     & $0.2326$   & $14.5570 \pm 0$      & $0.4094$   & $28.4810 \pm 0$          & $0.2033$   & $24.0506 \pm 0$      & $0.4884$   & $25.3165 \pm 0$\\
      SVM (RBF) + kmeans          & $34.5382$  & $\z{8.8608} \pm 0$             & $43.0936$  & $29.7468 \pm 0$     & $110.589$  & $\z{0.6329} \pm 0$   & $112.945$  & $\z{1.2658} \pm 0$       & $38.7497$  & $22.7848 \pm 0$      & $14.1561$  & $27.2152 \pm 0$\\
      SVM (sigmoid) + kmeans      & $4.0277$   & $22.6582 \pm 0$                & $8.0918$   & $17.7848 \pm 0$     & $0.7529$   & $25.3165 \pm 0$      & $0.7967$   & $12.0253 \pm 0$          & $0.6921$   & $17.7215 \pm 0$      & $0.4013$   & $28.4810 \pm 0$\\     
      \bottomrule
      \end{tabular}
    }
    \label{table:Arrhythmia_result}
      \vspace{-\baselineskip}
  \end{table*}

  \begin{table*}[htb]
    \newcommand{\z}{\phantom{0}}
    \caption{\textsc{Comparison of Classification Techniques. (gene expression cancer RNA-Seq dataset)}}
      \vspace{-\baselineskip}
    \resizebox{\textwidth}{!}{
      \begin{tabular}{@{}lcccccccccccc@{}}\toprule
        Method                  & \multicolumn{2}{c}{Raw}        & \multicolumn{2}{c}{Normalized}     & \multicolumn{2}{c}{PCA-30}                & \multicolumn{2}{c}{PCA-30 Normalized} & \multicolumn{2}{c}{AE-30}         & \multicolumn{2}{c}{AE-30 Normalized} \\ 
        \cmidrule(lr){2-3}\cmidrule(lr){4-5}\cmidrule(lr){6-7}\cmidrule(lr){8-9}\cmidrule(lr){10-11}\cmidrule(lr){12-13}
                                & Search (s) & acc               & Search (s) & acc                   & Search (s) & acc                          & Search (s) & acc                      & Search (s) & acc                  & Search (s) & acc            \\ \midrule
      KNN-Brute-Force + DBSCAN  & $14.5101$  & $59.0361 \pm 0$   & $10.3013$  & $\bf{66.5663} \pm 0$  & $0.0224$   & $94.5783 \pm 0$              & $0.0237$   & $78.3133 \pm 0$          & $0.0258$   & $\bf{64.4578} \pm 0$ & $0.0235$   & $59.3373 \pm 0$\\
      SVM (linear) + DBSCAN     & $124.593$  & $61.7470 \pm 0$   & $610.6730$ & $\z{9.9398} \pm 0$    & $0.6466$   & $\z{9.9398} \pm 0$           & $0.1193$   & $10.5422 \pm 0$          & $0.1407$   & $63.2530 \pm 0$      & $0.1122$   & $13.5542 \pm 0$\\
      SVM (polynomial) + DBSCAN & $81.6495$  & $61.7470 \pm 0$   & $86.6406$  & $\z{1.2048} \pm 0$    & $0.2585$   & $64.4578 \pm 0$              & $0.3012$   & $61.1446 \pm 0$          & $0.2013$   & $63.2530 \pm 0$      & $0.2056$   & $50.3012 \pm 0$\\
      SVM (RBF) + DBSCAN        & $X$        & $X$               & $X$        & $X$                   & $12.5077$  & $\z{9.9398} \pm 0$           & $3.8838$   & $63.2530 \pm 0$          & $5.0461$   & $40.3614 \pm 0$      & $11.4194$  & $49.6988 \pm 0$\\
      SVM (sigmoid) + DBSCAN    & $X$        & $X$               & $X$        & $X$                   & $0.6372$   & $71.6867 \pm 0$              & $0.8222$   & $65.9639 \pm 0$          & $0.6236$   & $44.2771 \pm 0$      & $0.2273$   & $38.2530 \pm 0$\\
      KNN-Brute-Force + kmeans  & $22.754$   & $\bf{74.0964} \pm 0$& $6.36577$& $53.6145 \pm 0$       & $0.0212$   & $\bf{94.8795} \pm 0$         & $0.0214$   & $\bf{84.9398} \pm 0$     & $0.0214$   & $42.1687 \pm 0$      & $0.0220$   & $\bf{65.9639} \pm 0$\\
      SVM (linear) + kmeans     & $136.408$  & $61.7470 \pm 0$   & $664.2860$ & $\z{9.9398} \pm 0$    & $0.5914$   & $\z{9.9398} \pm 0$           & $0.1077$   & $10.5422 \pm 0$          & $0.1274$   & $63.2530 \pm 0$      & $0.1084$   & $13.2530 \pm 0$\\
      SVM (polynomial) + kmeans & $81.4276$  & $61.7470 \pm 0$   & $81.1669$  & $63.8554 \pm 0$       & $0.2003$   & $64.4578 \pm 0$              & $0.2167$   & $25.3012 \pm 0$          & $0.1780$   & $63.2530 \pm 0$      & $0.1930$   & $50.3012 \pm 0$\\
      SVM (RBF) + kmeans        & $1772.32$  & $\z{9.9398} \pm 0$& $1800.6$   & $\z{9.9398} \pm 0$    & $1.3625$   & $\z{9.9398} \pm 0$           & $1.3848$   & $\z{9.9398} \pm 0$       & $11.1729$  & $39.7590 \pm 0$      & $4.7882$   & $28.6145 \pm 0$\\
      SVM (sigmoid) + kmeans    & $190.866$  & $26.5060 \pm 0$   & $81.7487$  & $63.8554 \pm 0$       & $0.8287$   & $65.9639 \pm 0$              & $0.4269$   & $65.9639 \pm 0$          & $0.9908$   & $28.9157 \pm 0$      & $0.2360$   & $39.4578 \pm 0$\\
      \bottomrule
      \end{tabular}
    }
    \label{table:gene_expression_result}
      \vspace{-\baselineskip}
  \end{table*}
